### 2023-03-13 proofs/main.tex
Add more contexts

% vim: ft=tex
\documentclass[a4,natbib=false]{article}
\usepackage[a4paper, total={8in, 10in}]{geometry}
\usepackage{hyperref}
\usepackage{mathpartir}

@@

Unification solution is represented by a list of unification solution entries.
Each entry restrict an unification variable in two possible ways: either stating
that it must be equivalent to a certain type ($[[pua :≈ iP]]$ or $[[nua :≈
iN]]$) or that it must be a (positive) supertype of a certain type ($[[pua :≥
iP]]$).

@@

>>>>

\UseRawInputEncoding
% vim: ft=tex
\documentclass[a4,natbib=false]{article}
\usepackage[a4paper, total={8in, 10in}]{geometry}
\usepackage{hyperref}
\usepackage{mathpartir}

@@

Unification solution is represented by a list of unification solution entries.
Each entry restrict an unification variable in two possible ways: either stating
that it must be equivalent to a certain type ($[[Δ ⊢ pua :≈ iP]]$ or $[[Δ ⊢ nua :≈
iN]]$) or that it must be a (positive) supertype of a certain type ($[[Δ ⊢ pua :≥
iP]]$).

@@

\subsection{Subtyping}

\input{../_build/_gen/tex/subtyping-lemmas.tex}
